Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-16 paper/v2.0/sections/appendix_c.tex
Add new version of the paper
Correct spellings

For our scenario, we take into account a time-independent total perturbation $V(\vb{r})$ which has been turned on at the reference time $t=t_0$, and the $t$-$t'$-Schrödinger equation becomes
\begin{equation} \label{eq_c5}
  i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')} =
  \qty[H_F(t') + V(\vb{r})]\ket{\Psi_{n,m}(t,t')}.
\end{equation}
This introduces a new wave function solution $\ket{\Psi_{n,m}}$ for a system with a given perturbation. If $t\leq t_0$, both of the solutions for Eq.~(\ref{eq_c2}) and Eq.~(\ref{eq_c5}) coincide
\begin{equation} \label{eq_c6}
  \ket{\psi_{n,m}(t,t')} =\ket{\Psi_{n,m}(t,t')} \quad
  \text{when} \quad
  t \leq t_0.
\end{equation}
Next, our analysis can move into the interaction picture representation \cite{bruus04,mahan00} and in the interaction picture, the $t$-$t'$-Floquet state can be identified as
\begin{equation} \label{eq_c7}
  \ket{\Psi_{n,m}(t,t')}_I = U_0^{\dagger}(t,t_0;t')
  \ket{\Psi_{n,m}(t,t')}.
\end{equation}
Due to time independence, the perturbation in the interaction picture has the same form as Schrödinger picture representation
\begin{equation} \label{eq_c8}
  V_I(\vb{r}) = U_0^{\dagger}(t,t_0;t')V(\vb{r})U_0(t,t_0;t') =
  V(\vb{r}).
\end{equation}
This leads us to the $t$-$t'$-Schrödinger equation in the interaction picture representation
\begin{equation} \label{eq_c9}
  i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')}_I =
  V_I(\vb{r})\ket{\Psi_{n,m}(t,t')}_I,
\end{equation}
with the recursive solutions \cite{bruus04,mahan00}
\begin{equation} \label{eq_c10}
  \begin{aligned}
  \ket{\Psi_{n,m}(t,t')}_I = &\ket{\Psi_{n,m}(t_0,t')}_I \\
  &+
  \frac{1}{i\hbar}
  \int_{t_0}^t dt_1 \;
  V_I(\vb{r}) \ket{\Psi_{n,m}(t_1,t')}_I.
  \end{aligned}
\end{equation}
Iterating the solution only up to the first order (Born approximation) we obtain
\begin{equation} \label{eq_c11}
  \begin{aligned}
    \ket{\Psi_{n,m}(t,t')}_I \approx &\ket{\psi_{n,m}(t_0,t')} \\
    &+
    \frac{1}{i\hbar}
    \int_{t_0}^t dt_1 \;
    V_I(\vb{r}) \ket{\psi_{n,m}(t_0,t')}.
  \end{aligned}
\end{equation}

@@

Next, we consider a scattering phenomenon when a electron scatters from a known $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into a distinct $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ with a constant quansienergy $\varepsilon$ as follows
\begin{equation} \label{eq_c15}
  \begin{aligned}
  \ket{\psi_{\beta}(t,t')} &= \exp(-\frac{i}{\hbar}\varepsilon_{\beta} t)
  \ket{\phi_{\beta}(t')} \\
  &
  \xRightarrow{\text{scattering}}
  \ket{\Psi_{\alpha}(t,t')} = \exp(-\frac{i}{\hbar}\varepsilon t)
  \ket{\Phi_{\alpha}(t')}.
  \end{aligned}
\end{equation}
\begin{figure}[b]
  \includegraphics[scale=1.0]{figures/fig_2.pdf}
  \caption{Scattering from known $\ket{\psi_{\beta}(t,t')}$ state to a constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to the scattering potential created by impurities in the material.}
  \label{fig_2}
\end{figure}
This scenario is illustared in Fig.~\ref{fig_2}.
The scattering amplitude for this scattering scenario can be calculated using the equation derived in Eq.~(\ref{eq_c14})
\begin{equation} \label{eq_c16}
  \begin{aligned}
    a_{\alpha\beta}(t,t') =
    -\frac{i}{\hbar}
    \int_{0}^t dt_1 \;
    e^{\frac{i}{\hbar}\qty(\varepsilon_{\beta} - \varepsilon)t_1}
    \bra{\phi_{\beta}(t')}
    V(\vb{r}) \ket{\phi_{\alpha}(t')}.
  \end{aligned}
\end{equation}
By assuming for a long time $t \rightarrow \infty$, we can turn this integral into a delta distribution
\begin{equation} \label{eq_c17}
  \begin{aligned}
    a_{\alpha\beta}(t') =
    -2\pi i \delta(\varepsilon_{\beta} - \varepsilon)Q,
  \end{aligned}
\end{equation}
where $Q = \bra{\phi_{\beta}(t')}
V(\vb{r}) \ket{\phi_{\alpha}(t')}$ and using the completeness properties we can re-write this as
\begin{equation} \label{eq_c18}
    Q =
    \sum_{\vb{k}}\sum_{\vb{k'}}
    \braket{\phi_{\beta}(t')}{\vb{k'}}
    \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}
    \braket{\vb{k}}{\phi_{\alpha}(t')}.
\end{equation}
Moreover, separating $x$-directional and $y$-directional momentum components, this can be simplified as
\begin{equation} \label{eq_c19}
    Q =
    \sum_{k_x}\sum_{{k'}_x}
    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} dk_y d{k'}_y \;
    V_{\vb{k'},\vb{k}}
    \phi_{\beta}^{\dagger}(\vb{k'},t')
    \phi_{\alpha}(\vb{k},t'),
\end{equation}
with $V_{\vb{k'},\vb{k}} \equiv \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}$.

Since we are presenting the the perturbation potential $V(\vb{r})$ by a group of randomly distributed impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed at randomly but in fixed positions $\vb{r}_i$. Then scattering potential $V(\vb{r})$ can be identified as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
\begin{equation} \label{eq_c20}
  V(\vb{r}) \equiv
  \sum_{i=1}^{N_{imp}}
  \upsilon (\vb{r}-\vb{r}_i).
\end{equation}
Furthermore, we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average. This model is characterized by \cite{akkermans10}
\begin{subequations}
\begin{equation} \label{eq_c21a}
  \expval{\upsilon(\vb{r})}_{imp} =0,
\end{equation}
\begin{equation} \label{eq_c21b}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'}),
\end{equation}
\end{subequations}
where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function depends only on $\vb{r}-\vb{r'}$. In addition, this model assumes that $\upsilon (\vb{r}-\vb{r'})$ only depends on the magnitude of the position difference $|\vb{r}-\vb{r'}|$, and it decays with a characteristic length $r_c$. Since this study considers the case where the wavelength of radiation or scattering electron is much greater than $r_c$, it is a better approximation to make two-point correlation function to be
\begin{equation} \label{eq_c22}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'}),
\end{equation}
where $\Upsilon_{imp}^2$ is a conatant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately model the total scattering potential as
\begin{equation} \label{eq_c23}
  V(\vb{r}) =
  \sum_{i=1}^{N_{imp}}
  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
\end{equation}
Here we can identify the $\Upsilon_{imp}$ as the strength of the delta potential.
Furthermore, we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
\begin{subequations} \label{eq_c24}
\begin{align}
 V_{\vb{k'},\vb{k}} & =
 \mel**{\vb{k'}}{\sum_{i=1}^{N_{imp}}
 \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i)}{\vb{k}} \label{eq_c24a} \\
 & =
 \sum_{i=1}^{N_{imp}}
 \int_{-\infty}^{\infty} dy\; \bigg[
 \frac{1}{\sqrt{L_xL_y}} e^{ik'_y y} \delta(y-y_i) \nonumber \\
 & \quad\times \frac{1}{\sqrt{L_xL_y}} e^{-i{k}_y y}
 \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \bigg] \label{eq_c24b} \\
  & =
 \sum_{i=1}^{N_{imp}} \frac{1}{{L_xL_y}}
 e^{i(k'_y - k_y )y}
 \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \label{eq_c24c}.
\end{align}
\end{subequations}
Since $\upsilon (\vb{r})$ in momentum space is a constant value, each impurity  produce same impurity potential for every $x$-directional momentum pairs. Additionally, assuming the total number of scatters $N_{imp}$ is microscopically large, we can derive
\begin{subequations} \label{eq_c25}
  \begin{align}
    V_{\vb{k'},\vb{k}}
    & =
    V_{k'_x,k_x}
    \frac{N_{imp}}{L_y L_x} \int_{-\infty}^{\infty} dy_i\;
    e^{i\qty({k'}_y - k_y)y_i} \label{eq_c25a} \\
    & =
    \eta_{imp} V_{k'_x,k_x} \delta(k'_y - k_y). \label{eq_c25b}
  \end{align}
\end{subequations}
In the above equation we introduced
\begin{equation} \label{eq_c26}
  V_{{k'}_x,k_x} \equiv
  \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x},
\end{equation}
which is a constant value for every $i$ impurity. Moreover, $\eta_{imp}$ is the number of impurities in a unit area. It is important to note that $\braket{x}{k_x} = e^{-ik_xx}$.

>>>>

For our scenario, we take into account a time-independent total perturbation $V(\vb{r})$ which has been turned on at the reference time $t=t_0$, and the $t$-$t'$-Schrödinger equation becomes
\begin{equation} \label{eq_c5}
  i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')} =
  \qty[H_F(t') + V(\vb{r})]\ket{\Psi_{n,m}(t,t')}.
\end{equation}
This introduces a new wave function solution $\ket{\Psi_{n,m}}$ for a system with a given perturbation. If $t\leq t_0$, both of the solutions for Eq.~(\ref{eq_c2}) and Eq.~(\ref{eq_c5}) coincide
\begin{equation} \label{eq_c6}
  \ket{\psi_{n,m}(t,t')} =\ket{\Psi_{n,m}(t,t')} \quad
  \text{when} \quad
  t \leq t_0.
\end{equation}
Next, our analysis can move into the interaction picture representation \cite{bruus04,mahan00} and in the interaction picture, the $t$-$t'$-Floquet state can be identified as
\begin{equation} \label{eq_c7}
  \ket{\Psi_{n,m}(t,t')}_I = U_0^{\dagger}(t,t_0;t')
  \ket{\Psi_{n,m}(t,t')}.
\end{equation}
Due to time-independence, the perturbation in the interaction picture has the same form as Schrödinger picture representation
\begin{equation} \label{eq_c8}
  V_I(\vb{r}) = U_0^{\dagger}(t,t_0;t')V(\vb{r})U_0(t,t_0;t') =
  V(\vb{r}).
\end{equation}
This leads us to the $t$-$t'$-Schrödinger equation in the interaction picture representation
\begin{equation} \label{eq_c9}
  i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')}_I =
  V_I(\vb{r})\ket{\Psi_{n,m}(t,t')}_I,
\end{equation}
with the recursive solutions \cite{bruus04,mahan00}
\begin{equation} \label{eq_c10}
  \begin{aligned}
  \ket{\Psi_{n,m}(t,t')}_I = &\ket{\Psi_{n,m}(t_0,t')}_I \\
  &+
  \frac{1}{i\hbar}
  \int_{t_0}^t dt_1 \;
  V_I(\vb{r}) \ket{\Psi_{n,m}(t_1,t')}_I.
  \end{aligned}
\end{equation}
Iterating the solution only up to the first order (Born approximation) we obtain
\begin{equation} \label{eq_c11}
  \begin{aligned}
    \ket{\Psi_{n,m}(t,t')}_I \approx &\ket{\psi_{n,m}(t_0,t')} \\
    &+
    \frac{1}{i\hbar}
    \int_{t_0}^t dt_1 \;
    V_I(\vb{r}) \ket{\psi_{n,m}(t_0,t')}.
  \end{aligned}
\end{equation}

@@

Next, we consider a scattering phenomenon when a electron scatters from a known $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into a distinct $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ with a constant quansienergy $\varepsilon$ as follows
\begin{equation} \label{eq_c15}
  \begin{aligned}
  \ket{\psi_{\beta}(t,t')} &= \exp(-\frac{i}{\hbar}\varepsilon_{\beta} t)
  \ket{\phi_{\beta}(t')} \\
  &
  \xRightarrow{\text{scattering}}
  \ket{\Psi_{\alpha}(t,t')} = \exp(-\frac{i}{\hbar}\varepsilon t)
  \ket{\Phi_{\alpha}(t')}.
  \end{aligned}
\end{equation}
\begin{figure}[b]
  \includegraphics[scale=1.0]{figures/fig_2.pdf}
  \caption{Scattering from known $\ket{\psi_{\beta}(t,t')}$ state to a constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to the scattering potential created by impurities in the material.}
  \label{fig_2}
\end{figure}
This scenario is illustrated in Fig.~\ref{fig_2}.
The scattering amplitude for this scattering scenario can be calculated using the equation derived in Eq.~(\ref{eq_c14})
\begin{equation} \label{eq_c16}
  \begin{aligned}
    a_{\alpha\beta}(t,t') =
    -\frac{i}{\hbar}
    \int_{0}^t dt_1 \;
    e^{\frac{i}{\hbar}\qty(\varepsilon_{\beta} - \varepsilon)t_1}
    \bra{\phi_{\beta}(t')}
    V(\vb{r}) \ket{\phi_{\alpha}(t')}.
  \end{aligned}
\end{equation}
By assuming for a long time $t \rightarrow \infty$, we can turn this integral into a delta distribution
\begin{equation} \label{eq_c17}
  \begin{aligned}
    a_{\alpha\beta}(t') =
    -2\pi i \delta(\varepsilon_{\beta} - \varepsilon)Q,
  \end{aligned}
\end{equation}
where $Q = \bra{\phi_{\beta}(t')}
V(\vb{r}) \ket{\phi_{\alpha}(t')}$ and using the completeness properties we can re-write this as
\begin{equation} \label{eq_c18}
    Q =
    \sum_{\vb{k}}\sum_{\vb{k'}}
    \braket{\phi_{\beta}(t')}{\vb{k'}}
    \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}
    \braket{\vb{k}}{\phi_{\alpha}(t')}.
\end{equation}
Moreover, separating $x$-directional and $y$-directional momentum components, this can be simplified as
\begin{equation} \label{eq_c19}
    Q =
    \sum_{k_x}\sum_{{k'}_x}
    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} dk_y d{k'}_y \;
    V_{\vb{k'},\vb{k}}
    \phi_{\beta}^{\dagger}(\vb{k'},t')
    \phi_{\alpha}(\vb{k},t'),
\end{equation}
with $V_{\vb{k'},\vb{k}} \equiv \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}$.

Since we are presenting the the perturbation potential $V(\vb{r})$ by a group of randomly distributed impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed at randomly but in fixed positions $\vb{r}_i$. Then scattering potential $V(\vb{r})$ can be identified as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
\begin{equation} \label{eq_c20}
  V(\vb{r}) \equiv
  \sum_{i=1}^{N_{imp}}
  \upsilon (\vb{r}-\vb{r}_i).
\end{equation}
Furthermore, we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average. This model is characterized by \cite{akkermans10}
\begin{subequations}
\begin{equation} \label{eq_c21a}
  \expval{\upsilon(\vb{r})}_{imp} =0,
\end{equation}
\begin{equation} \label{eq_c21b}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'}),
\end{equation}
\end{subequations}
where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function depends only on $\vb{r}-\vb{r'}$. In addition, this model assumes that $\upsilon (\vb{r}-\vb{r'})$ only depends on the magnitude of the position difference $|\vb{r}-\vb{r'}|$, and it decays with a characteristic length $r_c$. Since this study considers the case where the wavelength of radiation or scattering electron is much greater than $r_c$, it is a better approximation to make two-point correlation function to be
\begin{equation} \label{eq_c22}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'}),
\end{equation}
where $\Upsilon_{imp}^2$ is a constant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately model the total scattering potential as
\begin{equation} \label{eq_c23}
  V(\vb{r}) =
  \sum_{i=1}^{N_{imp}}
  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
\end{equation}
Here we can identify the $\Upsilon_{imp}$ as the strength of the delta potential.
Furthermore, we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
\begin{subequations} \label{eq_c24}
\begin{align}
 V_{\vb{k'},\vb{k}} & =
 \mel**{\vb{k'}}{\sum_{i=1}^{N_{imp}}
 \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i)}{\vb{k}} \label{eq_c24a} \\
 & =
 \sum_{i=1}^{N_{imp}}
 \int_{-\infty}^{\infty} dy\; \bigg[
 \frac{1}{\sqrt{L_xL_y}} e^{ik'_y y} \delta(y-y_i) \nonumber \\
 & \quad\times \frac{1}{\sqrt{L_xL_y}} e^{-i{k}_y y}
 \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \bigg] \label{eq_c24b} \\
  & =
 \sum_{i=1}^{N_{imp}} \frac{1}{{L_xL_y}}
 e^{i(k'_y - k_y )y}
 \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \label{eq_c24c}.
\end{align}
\end{subequations}
Since $\upsilon (\vb{r})$ in momentum space is a constant value, each impurity  produce same impurity potential for every $x$-directional momentum pairs. Additionally, assuming the total number of scatters $N_{imp}$ is microscopically large, we can derive
\begin{subequations} \label{eq_c25}
  \begin{align}
    V_{\vb{k'},\vb{k}}
    & =
    V_{k'_x,k_x}
    \frac{N_{imp}}{L_y L_x} \int_{-\infty}^{\infty} dy_i\;
    e^{i\qty({k'}_y - k_y)y_i} \label{eq_c25a} \\
    & =
    \eta_{imp} V_{k'_x,k_x} \delta(k'_y - k_y). \label{eq_c25b}
  \end{align}
\end{subequations}
In the above equation we introduced
\begin{equation} \label{eq_c26}
  V_{{k'}_x,k_x} \equiv
  \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x},
\end{equation}
which is a constant value for every $i$ impurity. Moreover, $\eta_{imp}$ is the number of impurities in a unit area. It is important to note that $\braket{x}{k_x} = e^{-ik_xx}$.
